\textls[-0]{\thetitle}

### 2023-03-21 coqimpl.tex
tweak in §5

What seems to require more thought from a language-design perspective is the
restriction that recursion and induction (on extensible types) cannot be nested.
%and must be at the top level through the \lsti{FRecursion} and \lsti{FInduction}
%commands.
A possible solution is to make the plugin generate proof obligations for
nested pattern matches when the inductive types acquire new constructors.
%
Also limiting---and interesting for future research---is
that generated propositional equalities cannot be used by Coq to automatically
reduce terms to definitionally equal forms, which causes inconveniences for
developments using intrinsically typed syntax.

>>>>

What seems to require more thought from a language-design perspective is the
restriction that recursion and induction (on extensible types) cannot be nested.
%and must be at the top level through the \lsti{FRecursion} and \lsti{FInduction}
%commands.
A possible solution is to make the plugin generate proof obligations for
nested pattern matches when the inductive types acquire new constructors.
%
Also interesting for future research is the support for automatically converting
terms to propositionally equally typed forms using generated propositional equalities.
The lack of this automation currently may cause inconveniences for
developments using intrinsically typed syntax.
